Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-12-03 02_Paper/paper.tex
ml update.

\subsection{Support Vector Machines}
Support Vector Machines (SVM) offer a convex alternative to MLPs \cite{Suykens2002least}.
A convex classifier is guaranteed to converge to a global solution regardless 
of its initialization. 
The Kernel trick allows SVM to solve non-linear classification problems \cite{Suykens2002least} by mapping implicitly mapping the inputs into a higher feature space. Radial basis functions (RBF) are commonly chosen as kernels
\cite{Suykens2002least} we choose to follow this practice as well.

\subsection{Decision Tree}
Decision trees are binary trees, these binary trees work with the input
features at the roots, resulting decisions are found by moving
trough the tree to top leaves. At every branch in the tree a decision
is made, until one arrives at the final conclusion \cite{Marsland2015Machine}.
Decision trees are trained using  
\MW{Will write more tomorrow.}

@@

Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle. For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and discarded if so. At this point we have a series de data-samples, which each of them is based in time series. However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.

>>>>

\subsection{Support Vector Machines}
Support Vector Machines (SVM) attempt to separate data
along hyperplanes \cite{aggarwal2015data}. 
SVM offer a convex alternative to MLPs \cite{Suykens2002least}.
A convex classifier is guaranteed to converge to a global solution
regardless of its initialization.
Non-separable data can become separable if projected to a different
possibly high dimensional space trough a Kernel function.
The Kernel trick allows SVM to solve some non-linear
classification problems \cite{Suykens2002least}
Radial basis functions (RBF) are commonly chosen as kernels
\cite{Suykens2002least} we choose to follow this practice as well.

\subsection{Decision Tree}
Decision trees are binary trees, these binary trees work with the input
features at the roots, decisions are made by moving
up the tree to top leaves. At every branch in the tree, a decision
is made, until one arrives at the decision \cite{Marsland2015Machine}.
For numerical input features, each decision partitions the data
\cite{aggarwal2015data}. For example by comparison to a threshold value.
To construct the tree these cutoff values have to be chosen
at every branch. The construction problem turns into an optimization 
problem when a split criterion is introduced. Common choices are 
cross-entropy of Gini-coefficient \cite{aggarwal2015data}.
During construction, the chosen function must be minimized.

@@

Once the data is clean and compiled in one directory, the next step would be to split the data based on the assembly cycle. For our purposed, we split the dataset in individual data-samples with help of the action tags included in the dataset Table.~\ref{tab:data_source}. Subsequently, each data-sample is automatically checked for missing sensor values and diskarded if so. At this point we have a series de data-samples, which each of them is based in time series. However, we are not interested in a time series analysis, therefore it would be needed to compress each time-series based data-sample in an atemporal data-sample.
